Meta-analysis of the Interoceptive Accuracy Scale

### 2025-02-03 analysis/study2.qmd
used scales
till df10a (need to check the ones after)

>>>>

## Average Correlations

- BPQ - sf - Body perception questionnaire short form
- BPQ - vsf - Body perception questionnaire very short form 
- BVAQ - Bermond–Vorst Alexithymia Questionnaire 
- MAIA-2 - Multidimensional Assessment of Interoceptive Awareness , Version-2
- ICQ  - Interocpetive Confusion Questionnaire
- TAS - Toronto Alexithymia Scale 
- BAQ - Body awareness questionnaire
- BRS - the body responsiveness scale 
- PHQ-2 - Patient Health Questionnaire 2 items on major depressive episodes 
- PHQ-4 - atient Health Questionnaire 4 items assessing anxiety and depression 
- PHQ-9 - Patient Health Questionnaire 9-Item Version assesses depressive symptoms
- PHQ-15 - Patient Health Questionnaire 15-Item Version assesses Somatic symptom distress 
- SSS-8 - Somatic Symptom Scale 
- IATS - Interoceptive Attention Scale
- GAD-2 - Generalized Anxiety Disorder Scale 2 items on anxiety disorder 
- STAIT - State-Trait-Anxiety Inventory Trait subscale
- FFMQ - Observation and Description subscales of the Five Facet Mindfulness Questionnaire
- NEOFFI - Neuroticism Neo Five-Factor Inventory Neuroticism subscale
- ASI - Anxiety Sensitivity Inventory 3
- BDI - The Beck Depression Inventory
- EDI_IA - Eating Disorder Inventory, interoceptive awareness subscale
- BFI -  Big Five inventory-10
- ASQ -  Autism-Spectrum Quotient
- MSI-BPD - Mclean Screening Instrument for Borderline Personality Disorder
- GCB - Generic Conspiracist Beliefs scale
- IPIP6 - Mini International Personality Item Pool
- PI - Primal Inventory 18 items and 99 items 
- PID5-sf - Personality Inventory for DSM-5 Short Form 
- SPQ-BRU - Schizotypal Personality Questionnaire, brief revised updated
- LIE - Lying Profile Questionnaire
